---
title: "hunger"
author: "issa fall"
date: "March 7, 2016"
output: html_document
---

##hunger dataset
```{r,echo=TRUE}
hunger<-read.csv("http://apps.who.int/gho/athena/data/GHO/WHOSIS_000008.csv? profile= text&filter =
COUNTRY::SEX:")
head(hunger)
str(hunger)
summary(hunger)
hunger<-hunger[hunger$SEX != "BTSX", ]
head(hunger)
tail(hunger)
str(hunger)
```
##Plot % hungry versus time
```{r,echo=TRUE}
lm<-lm(hunger$Numeric ~ hunger$YEAR)
plot(hunger$YEAR, hunger$Numeric, pch =19, col ="blue")
points(hunger$YEAR, hunger$Numeric, pch =19, col =((hunger$SEX == "MLE")*1+1))
```


##Color by male and female
```{r,echo=TRUE}
lmM<-lm(hunger$Numeric[hunger$SEX == "MLE"] ~ hunger$YEAR[hunger$SEX == "MLE"])
lmM
lmF<-lm(hunger$Numeric[hunger$SEX == "FMLE"] ~ hunger$YEAR[hunger$SEX == "FMLE"])
lmF
plot(hunger$YEAR, hunger$Numeric, pch =19)
points(hunger$YEAR, hunger$Numeric, pch =19,col =((hunger$SEX =="MLE")*1+1))
lines(hunger$YEAR[hunger$SEX == "MLE"], lmM$fitted, col ="black",lwd =3)
lines(hunger$YEAR[hunger$SEX == "FMLE"], lmF$fitted, col ="red", lwd =3)
```

##Two lines,same slope in R
```{r,echo=TRUE}
lmBoth<-lm(hunger$Numeric ~ hunger$YEAR + hunger$SEX)
lmBoth
plot(hunger$YEAR, hunger$Numeric,pch =19)
points(hunger$YEAR, hunger$Numeric, pch =19, col =((hunger$SEX == "MLE")*1+1))
abline(c(lmBoth$coeff[1], lmBoth$coeff[2]),col ="red", lwd =3)
abline(c(lmBoth$coeff[1] + lmBoth$coeff[3], lmBoth$coeff[2]), col ="black", lwd =3)
sn<-hunger[hunger$COUNTRY == "SEN", ]
sn
summary(sn)
     


